---
title: "p8105_hw3_ac4964"
author: "AnMei Chen"
date: "10/13/2021"
output: github_document
---

# Problem 1

```{r }
library(tidyverse)
library(p8105.datasets)
library(reshape2)
data("instacart")

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis" , 
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

The dataset of instacart contains data of `r max(instacart$order_id)` orders from instacart. It contains a total of `r nrow(instacart)` observations and `r ncol(instacart)` variables (`r colnames(instacart)`). An example of this dataset would be: `r head(instacart, 1)`


How many aisles are there, and which aisles are the most items ordered from?
```{r}
n_of_aisles = 
  instacart %>% 
  pull(aisle) %>% 
  factor() %>% 
  nlevels()

most_freq_aisles = 
  instacart %>% 
  group_by(aisle) %>%
  summarize(counts = n()) %>%
  arrange(desc(counts)) %>% 
  head(1)
```

There are `r n_of_aisles` aisles in this data set.
The aisles that the most items ordered from is the `r pull(most_freq_aisles, aisle)` aisle.


Make a plot that shows the number of items ordered in each aisle, limiting this to aisles with more than 10000 items ordered. Arrange aisles sensibly, and organize your plot so others can read it.

```{r}

aisles_10000 =
  instacart %>% 
  group_by(aisle) %>%
  summarize(counts = n()) %>% 
  filter(counts > 10000) %>% 
  mutate(
    aisle = factor(aisle),
    aisle = forcats::fct_reorder(aisle, counts, desc)
  )
 
ggplot(aisles_10000) + 
geom_histogram(aes(x = aisle, y = counts), stat = "identity") +
labs(
    title = "Number of Items Ordered In Each Aisle (Aisle > 10000)",
    x = "Aisle",
    y = "Counts",
  ) +
theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))

```


Make a table showing the three most popular items in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables fruits”. Include the number of times each item is ordered in your table.

```{r}
most_pop_of_bi =
  instacart %>%
  group_by(aisle,product_name) %>%
  filter(aisle == "baking ingredients" ) %>%
  summarize(counts = n()) %>% 
  arrange(desc(counts)) %>% 
  head(3)

most_pop_of_dfc =
  instacart %>% 
  group_by(aisle,product_name) %>%
  filter(aisle == "dog food care" ) %>%
  summarize(counts = n()) %>%
  arrange(desc(counts)) %>% 
  head(3)

most_pop_of_pvf =
  instacart %>% 
  group_by(aisle,product_name) %>%
  filter(aisle == "packaged vegetables fruits" ) %>%
  summarize(counts = n()) %>%
  arrange(desc(counts)) %>% 
  head(3)

most_pop_of_three = 
  bind_rows(most_pop_of_bi, most_pop_of_dfc,most_pop_of_pvf) %>%
  knitr::kable(digits = 2)

most_pop_of_three
```


Make a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week; format this table for human readers (i.e. produce a 2 x 7 table).

```{r}

apples_icecream =
  instacart %>% 
  filter(product_name == "Pink Lady Apples" | product_name == "Coffee Ice Cream") %>%
  group_by(product_name,order_dow) %>% 
  mutate(
    order_dow = factor(order_dow),
    order_dow = recode(order_dow, "0" = "Sunday", "1" = "Monday", "2" = "Tuesday", "3" = "Wendesday", "4" = "Thursday", "5" = "Friday", "6" = "Saturday"),
    order_dow = ordered(order_dow, levels = c("Sunday", "Monday", "Tuesday", "Wendesday","Thursday","Friday","Saturday"))
    ) %>% 
  summarize(mean_hour = mean(order_hour_of_day)) %>% 
  pivot_wider(
    names_from = "order_dow",
    values_from = "mean_hour"
    ) %>% 
  knitr::kable()
```


# Problem 2


```{r}
data("brfss_smart2010")

brfss_df = 
  brfss_smart2010 %>% 
  janitor::clean_names() %>% 
  filter(topic == "Overall Health") %>% 
  mutate(
    response = factor(response),
    response = ordered(response, levels = c("Poor", "Fair", "Good", "Very good", "Excellent")),
  ) %>% 
  rename( 
    state = locationabbr,
    county = locationdesc 
          )

levels(brfss_df$response)
  
```


In 2002, which states were observed at 7 or more locations? What about in 2010?

```{r}
colnames(brfss_df)

location_2002 = 
  brfss_df %>%
  filter(year == "2002") %>% 
  group_by(state) %>%  
  distinct(county) %>%  
  count(state) %>% 
  filter(n >= 7) %>% 
  arrange(n)

location_2010 = 
  brfss_df %>%
  filter(year == "2010") %>% 
  group_by(state) %>%  
  distinct(county) %>%  
  count(state) %>% 
  filter(n >= 7) %>% 
  arrange(n)


```


Construct a dataset that is limited to Excellent responses, and contains, year, state, and a variable that averages the data_value across locations within a state. Make a “spaghetti” plot of this average value over time within a state (that is, make a plot showing a line for each state across years – the geom_line geometry and group aesthetic will help).

```{r}

excellent_dataset =
  brfss_df %>% 
  filter(response == "Excellent") %>%
  select(c(year,state, data_value)) %>% 
  group_by(year, state) %>% 
  summarise_at( vars(average = data_value), funs(mean(., na.rm = TRUE))) %>% 
  ggplot(aes(x = year, y = average, color = state)) +
  geom_line()

```



Make a two-panel plot showing, for the years 2006, and 2010, distribution of data_value for responses (“Poor” to “Excellent”) among locations in NY State.

```{r}

distribution_plot =
  brfss_df %>% 
  filter(year == "2006" | year == "2010" , state == "NY") %>% 
  ggplot(aes(x = response, y = data_value)) +
  geom_boxplot() +
  facet_grid(. ~ year)


```


# Problem 3


```{r}
accel_df = 
  read_csv("data/accel_data.csv") %>% 
  janitor::clean_names() %>% 
  mutate(
    weekday_vs_weekend = recode(day, "Monday" = "Weekday", "Tuesday" = "Weekday","Wednesday" = "Weekday","Thursday" = "Weekday", "Friday" = "Weekday","Saturday" = "Weekend","Sunday" = "Weekend")
    ) %>% 
  relocate(week,day_id,weekday_vs_weekend)

```

The dataset of Accekerineters contains  `r max(accel_df$day_id)` days of accelerometer data collected on a 63 year-old male with BMI 25, who was admitted to the Advanced Cardiac Care Center of Columbia University Medical Center and diagnosed with congestive heart failure. It contains a total of `r nrow(accel_df)` observations and `r ncol(accel_df)` variables. 


Traditional analyses of accelerometer data focus on the total activity over the day. Using your tidied dataset, aggregate across minutes to create a total activity variable for each day, and create a table showing these totals. Are any trends apparent?

```{r}
total_act =
  accel_df %>%
  mutate(total_activity = rowSums(across(activity_1:activity_1440))) %>%
  select(c(day_id,total_activity)) %>%
  knitr::kable() 

total_act_plot =
  accel_df %>%
  mutate(total_activity = rowSums(across(activity_1:activity_1440))) %>%
  select(c(day_id,total_activity)) %>%
  ggplot(aes(x = day_id, y = total_activity)) +
  geom_line()
  
```


Accelerometer data allows the inspection activity over the course of the day. Make a single-panel plot that shows the 24-hour activity time courses for each day and use color to indicate day of the week. 

```{r}
hr_act_time_plot = 
  accel_df %>%
  mutate(
    day = factor(day),
    day = ordered(day, levels = c("Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday"))
  ) %>% 
  melt(id.vars = c("day_id","day")) %>% 
  ggplot(aes(x = as.integer(value), y = day_id, color = day)) +
  geom_line(alpha = .5) +
  scale_x_continuous(n.breaks = 10) +
  scale_y_continuous(n.breaks = 10) +
  labs(
    title = "24-Hour Activity Time Courses For Each Day",
    x = "Activity Counts For Each Minute",
    y = "Day",
  ) 
```

Describe in words any patterns or conclusions you can make based on this graph.

Most of the days the 24-hour acticity counts for each minute of this patient are ranging from 0 to 2500. Wednesday has the highest activity counts for each minute in a 24-hour day.